---
title: "Zindi Challenge Preprcosseing"
author: "Eric Wanjau"
toc: true
format: 
  html:
    number-sections: true
    toc-location: left
    code-tools: true
    code-fold: false
    code-link: true
editor: visual
execute: 
  eval: false
  warning: false
  message: false
---

## Description

::: callout-note
This is jus a preprocessing script for:

**Spot the Mask Challenge by[ #ZindiWeekendz](http://www.zindi.africa/)**

Link to challenge:

<https://zindi.africa/competitions/zindiweekendz-learning-spot-the-mask-challenge/data>
:::

The objective of this challenge is to create an image classification machine learning model to accurately predict the likelihood that an image contains a person wearing a face mask, or not.
The total dataset contains 1,800+ images of people either wearing masks or not.

You will need to use train_labels.csv to split the data into the train and test sets.

> `1` indicates an image with a person with a `mask`, `0` indicates a person `without a mask`.

## Splitting data into train and test sets

```{r}
# Load required packages
library(tidyverse)
library(here)

# Import train and test labels
train_labels <- read_csv("train_labels.csv")
test_files <- read_csv("SampleSubmission.csv") %>% 
  pull(image)

# Obtain train masked and nonmasked image files
# This can be done in a function: group_by + nest + map? if more categories?

masked <- train_labels %>% 
  filter(target == 1) %>% 
  pull(image)

nonmasked <- train_labels %>% 
  filter(target == 0) %>% 
  pull(image)

# How many masked images
length(masked)

# How many nonmasked images
length(nonmasked)

# How many test files
length(test_files)
```

## Place the images into their own folders

```{r}
# Image file names
all_files <- list.files("images")
```

```{r}

# Create train images folder
dir.create("train_images/masked")
dir.create("train_images/nonmasked")

# dir.exists("images")

# Create test folder
dir.create("test_images")

# Copy masked files from `images` folder into `train/masked` folder
invisible(file.copy(from = here("images", masked),
          to = here("train_images", "masked"),
          overwrite = TRUE))

# Copy unmasked files from `images` folder to `train/nonmasked` folder
invisible(file.copy(from = here("images", nonmasked),
          to = here("train_images", "nonmasked"),
          overwrite = TRUE))

# Copy test files into test folder
invisible(file.copy(from = here("images", test_files),
          to = here("test_images"),
          overwrite = TRUE))
```

```{r}
# Alternative solution for test files
# What are the test files
# Discard train files from all_files
test_files <- discard(all_files, all_files %in% train_labels$image)

# Copy test files into test folder
invisible(file.copy(from = here("images", test_files),
          to = here("test_images"),
          overwrite = TRUE))
```
